### 2010-12-14 docs/tex/model.tex
Frank has been changed to Franks

The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Frank and Noble. Their initial work \cite{franks2002} seems of focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.

On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Frank and Noble. Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics. So an evolutionary simulation to observe the above mentioned phenomenon has been presented in this piece of work.

Frank and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}. Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded. In this model prey colorations are free to evolve. This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.

\subsection{Models by Frank and Noble}
\label{subsec:models-by-frank-and-noble}
%Explain more about the first model by Frank and Noble
The \textbf{first} model by Frank and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}. Each individual had a single gene: a value representing their external appearance or phenotype. The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors). The distance of one phenotype from another represents their levels of similarity.

@@

The \textbf{second} model by Frank and Noble \cite{franks2003} is based on two working hypothesis:

@@

%Explain the results for the second model by Frank and Noble
\paragraph{Results}
According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established. There was existence of multiple mimicry rings of very different frequency (population). Second experiment was carried out with some palatable species along with the unpalatable ones which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out. It can be observed that,

@@

\subsection{Species diversity}
Frank and Noble have used different models to diversify species. In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

@@

This representation in table \ref{tab:genetic-representation-palatability} is unlike Frank and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.

>>>>

The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble. Their initial work \cite{franks2002} seems of focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.

On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble. Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics. So an evolutionary simulation to observe the above mentioned phenomenon has been presented in this piece of work.

Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}. Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded. In this model prey colorations are free to evolve. This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.

\subsection{Models by Franks and Noble}
\label{subsec:models-by-frank-and-noble}
%Explain more about the first model by Franks and Noble
The \textbf{first} model by Franks and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}. Each individual had a single gene: a value representing their external appearance or phenotype. The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors). The distance of one phenotype from another represents their levels of similarity.

@@

The \textbf{second} model by Franks and Noble \cite{franks2003} is based on two working hypothesis:

@@

%Explain the results for the second model by Franks and Noble
\paragraph{Results}
According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established. There was existence of multiple mimicry rings of very different frequency (population). Second experiment was carried out with some palatable species along with the unpalatable ones which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out. It can be observed that,

@@

\subsection{Species diversity}
Franks and Noble have used different models to diversify species. In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

@@

This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.

### 2010-12-14 docs/tex/result.tex
Frank has been changed to Franks

This experiment is an ideal scenario for observing Mullerian mimicry. As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population. From the second work of Frank and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium. But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them. By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.

@@

\section{Analysis of Mullerian Mimicry}
\label{sec:result-mullerian-mimicry}
Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}. For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance. The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four. So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern. But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings. It can be concluded that our results match with the one from Frank and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.

>>>>

This experiment is an ideal scenario for observing Mullerian mimicry. As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population. From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium. But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them. By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.

@@

\section{Analysis of Mullerian Mimicry}
\label{sec:result-mullerian-mimicry}
Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}. For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance. The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four. So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern. But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings. It can be concluded that our results match with the one from Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
